### 2023-03-31 reachable-resilience.tex
up
tableau
Ref added to tables

\begin{theorem}\cite{DBLP:conf/gg/Ozkan22,DBLP:journals/corr/abs-2108-00889}
{\sc bounded-state-resilience} and {\sc $k$-state-resilience} are decidable for WSTS $S$ with strong upward compatibility and such that $\uparrow \post^*(s)$ is computable for $s \in S$.
\end{theorem}

@@

\begin{theorem}
{\sc State-resilience} is undecidable for strongly compatible WSTS with effective pred-basis.
\end{theorem}

@@

\begin{corollary}
Bounded state-resilience and 
$k$ state-resilience are undecidable for strongly compatible WSTS with effective pred-basis.
\end{corollary}

@@

\begin{theorem}{(Adjusting Theorem 1 from \cite{DBLP:journals/corr/abs-2108-00889})}
{\sc Reachable-resilience} is decidable for (not necessarily strong) WSTS with effective 
$\uparrow$ $\post^*$ basis.
\end{theorem}

@@

@@

>>>>

\begin{theorem}\cite{DBLP:conf/gg/Ozkan22,DBLP:journals/corr/abs-2108-00889}\label{ref ozkan}
{\sc bounded-state-resilience} and {\sc $k$-state-resilience} are decidable for WSTS $S$ with strong upward compatibility and such that $\uparrow \post^*(s)$ is computable for $s \in S$.
\end{theorem}

@@

\begin{theorem}\label{srp up down}
{\sc State-resilience} is undecidable for strongly compatible WSTS with effective pred-basis.
\end{theorem}

@@

\begin{corollary}\label{bsrp up down}
Bounded state-resilience and 
$k$ state-resilience are undecidable for strongly compatible WSTS with effective pred-basis.
\end{corollary}

@@

\begin{theorem}{(Adjusting Theorem 1 from \cite{DBLP:journals/corr/abs-2108-00889})}\label{post srp}
{\sc Reachable-resilience} is decidable for (not necessarily strong) WSTS with effective 
$\uparrow$ $\post^*$ basis.
\end{theorem}

@@

But what if we are in the case of $\uparrow \post^*$ effectiveness?

@@

\mathieu{Should try to put all results in a single table}

With only strong compatibility hypothesis:

\begin{center}
\begin{tabular}{ | l | c | c | r |}
\hline   \Safe~\Bad & $\uparrow$~ $\downarrow$~ & $\downarrow$~ $\uparrow$~  \\ \hline
   SRP & Undecidable (Thm~\ref{srp up down}) & Undecidable  \\ \hline
   BSRP & Undecidable (Corollary~\ref{bsrp up down}) &  ??  \\ \hline
      kSRP & Undecidable (Corollary~\ref{bsrp up down}) & ?? \\ \hline
 \end{tabular}
\end{center}

With $\uparrow \post^*$ effectiveness hypothesis:

\begin{center}
\begin{tabular}{ | l | c | c | r |}
\hline   \Safe~\Bad & $\uparrow$~ $\downarrow$~ & $\downarrow$~ $\uparrow$~  \\ \hline
   SRP & Decidable (Thm~\ref{post srp}) & ??  \\ \hline
   BSRP & ?? &  ??  \\ \hline
      kSRP & ?? & ?? \\ \hline
 \end{tabular}
\end{center}

With $\uparrow \post^*$ effectiveness and strong compatibility hypothesis:

\begin{center}
\begin{tabular}{ | l | c | c | r |}
\hline   \Safe~\Bad & $\uparrow$~ $\downarrow$~ & $\downarrow$~ $\uparrow$~  \\ \hline
   SRP & Decidable (Thm~\ref{postcomputable})& ??  \\ \hline
   BSRP & Decidable (Thm~\ref{ref ozkan})&  ??  \\ \hline
      kSRP & Decidable (Thm~\ref{ref ozkan}) & ?? \\ \hline
 \end{tabular}
\end{center}
